Baseline centering problem

### 2018-12-21 paper/order_magnitude.tex
Very quick aside on rmsprop (probably needs a bit more caution)

Now assume that $\tilde{A}(s, a)$ is or order $\deltat$ with probability roughly $1 - \deltat$, and
of order $1$ with probability $\deltat$. Further assume that $\sigma$ is close to optimal, in the sense
that $\sigma$ is close to $1$ when $\tilde{A}$ is of order $\deltat$, and close to $0$ when $\tilde{A}$
is of order $1$. Under these assumptions, $\delta A_\phi$ is of order $\deltat^\sigma(s, a)$, and the
following orders of magnitudes for the gradients are obtained for $\phi^m$ and $\phi^M$
\begin{align}
	\delta_{\phi^m} \mathcal{L} \approx& \deltat\\
	\delta_{\phi^M} \mathcal{L} \approx& \deltat.
\end{align}
The gradient with respect to $\theta$ could be problematic. When $\deltat$ is small, the recall term
$\log{\deltat} \partial_\theta \sigma_\theta$ dominates, meaning that $\sigma wi

>>>>

Now assume that $\tilde{A}(s, a)$ is or order $\deltat$ with probability roughly $1 - \deltat$, and
of order $1$ with probability $\deltat$. Further assume that $\sigma$ is close to optimal, in the sense
that $\sigma$ is close to $1$ when $\tilde{A}$ is of order $\deltat$, and close to $0$ when $\tilde{A}$
is of order $1$. Under these assumptions, $\delta A_\phi$ is of order $\deltat^\sigma(s, a)$, and the
following orders of magnitudes for the gradients are obtained for $\phi^m$ and $\phi^M$
\begin{align}
	\delta_{\phi^m} \mathcal{L} \approx& \deltat\\
	\delta_{\phi^M} \mathcal{L} \approx& \deltat.
\end{align}
The gradient with respect to $\theta$ could be problematic. When $\deltat$ is small, the recall term
$\log{\deltat} \partial_\theta \sigma_\theta$ dominates. This gradient is always of order $1$. A
consequence is that we should avoid parameter sharing between $\theta$ and the other parameters, as
the gradient on $\sigma$ would almost always dominate.

\paragraph{An aside on the use of RMSProp}
Empirically, RMSProp helps a lot in term of convergence speed. Special care should be put on the batch
size when using RMSProp. Recall that RMSProp updates network parameters as
\begin{align}
	H &\leftarrow (1 - \alpha) H + \alpha \text{diag}(g \odot g)\\
	\phi &\leftarrow \phi - \eta H^{-1/2} g
\end{align}
with $g = \partial_\phi \mathcal{L}$.

With batch size $1$ or close to $1$, in
the one dimensional case and in term of orders of magnitude, for both $\phi^M$
and $\phi^m$, $g \approx B \deltat + (1 - B)$ with $B\sim \mathcal{B}(1 -
\deltat)$ a bernoulli with $\mathbb{P}(B = 1) = 1 - \deltat$. If the
expectation of $H$ reaches a stationnary regime, it is easily verifiable that
$\mathbb{E} H \approx \deltat$, and consequently that learning rates are divided
by $\sqrt{\deltat}$.

With batch sizes of order $1 / \deltat$, as the variance of $g$ is no longer of order
$\deltat$, but of order $\deltat^2$, learning rates are divided
by $\deltat$, resulting in update steps that are effectively of order $\eta$.
